Approximating Lattice Similarity

### 2023-02-07 LatticeMatching/LM.tex
fix Euclid reference instead of only Wikipedia

In Euclidean geometry, two objects are described as ``similar'' if they are identical except for a scale factor, see Euclid, in \cite{heath1956thirteen}.
	In crystallography, we can say that all face-centered cubic unit cells are similar (assuming
	that they are in the same presentation). On the other hand, not all primitive orthorhombic 
	unit cells are similar.  In a metric space, we
	refer to two objects as ``approximately similar'' if the distance between them after scaling
	to the same size is, in some sense, small, {\it e.g}. commensurate with the experimental errors
	in determination of the unit cells.  The algorithm below attempts to find the representation of one 
	cell that is nearest-to-similar to some other cell. For a given reference cell, the probe cell
	will be transformed to other choices of unit cell that would generate the probe's lattice, and the
	closest match to the reference will be chosen for the result. Finally, the lattice centering
	of the reference cell will be restored (if necessary).

>>>>

In Euclidean geometry, two objects are described as ``similar'' if they are identical except for a scale factor, see Euclid, in \cite{heath1956thirteen} and a longer description in Wikipedia  \cite{enwiki:1097100366}.
	In crystallography, we can say that all face-centered cubic unit cells are similar (assuming
	that they are in the same presentation). On the other hand, not all primitive orthorhombic 
	unit cells are similar.  In a metric space, we
	refer to two objects as ``approximately similar'' if the distance between them after scaling
	to the same size is, in some sense, small, {\it e.g}. commensurate with the experimental errors
	in determination of the unit cells.  The algorithm below attempts to find the representation of one 
	cell that is nearest-to-similar to some other cell. For a given reference cell, the probe cell
	will be transformed to other choices of unit cell that would generate the probe's lattice, and the
	closest match to the reference will be chosen for the result. Finally, the lattice centering
	of the reference cell will be restored (if necessary).
